### 2025-06-16 question_papers/aima104_first_in_sem.tex
question_aima104

\documentclass[12pt]{exam}
\usepackage{preamble_question}
\usepackage[normalem]{ulem}
\renewcommand\ULthickness{2pt}
\setlength\ULdepth{1.3ex}

\begin{document}

\begin{center}
 {\bfseries  {\Large Kathmandu University}} \\[1mm]
 First In-Semester Exam-2025\\[-1mm]
 {\small \textbf{Department of Artificial Intelligence, Panchkhal}}
\end{center}
\vskip 5mm

\begin{minipage}{0.70\linewidth}
  \begin{flushleft}
    Level: B.Tech Artificial Intelligence \\
    Year: I \\
    Time: 60 minutes
  \end{flushleft}
\end{minipage} \hfill
\begin{minipage}{0.25\linewidth}
  \begin{flushleft}
    Course: AIMA 104 \\
    Semester: II \\
    F.M. : 20
  \end{flushleft}
\end{minipage}
\vskip 2mm
\rule{\textwidth}{1pt}
\hskip 15mm \textit{Write the answer according to the mark allocated to it}. \textit{For short questions, write short answers, for long questions write long answers}.

\vskip 10mm

\begin{questions}
\question For a matrix $A$ of order $m \times n$. Show that $Null(A)$ is a subspace of $\mathbb{R}^n$. [2]

@@

  \question Describe the transformation of the following matrix geometrically:
  $\begin{bmatrix}
    1 & 0\\
    0 & 0
  \end{bmatrix}$. [2]

\question Prove: The transformation $T: V \to W$ is linear, then $T(0)=0$. [2]

@@

\question Solve: \hspace{2mm} $x_2+4x_3 = -5, \hspace{5mm} x_1+3x_2+5x_3 = -2, \hspace{5mm} 3x_1 + 7x_2 + 7x_3 = 6$. [4]

\end{questions}
\end{document}

>>>>

\documentclass[12pt]{exam}
\usepackage{preamble_question_small}
\usepackage[normalem]{ulem}
\renewcommand\ULthickness{2pt}
\setlength\ULdepth{1.3ex}

\begin{document}
\begin{center}
 {\bfseries  {\large Kathmandu University}} \\
 First In-Semester Exam-2025\\[-1mm]
 {\small \textbf{Department of Artificial Intelligence, Panchkhal}}
\end{center}

\begin{minipage}{0.70\linewidth}
  \begin{flushleft}
    Level: B.Tech Artificial Intelligence \\
    Year: I \\
    Time: 60 minutes
  \end{flushleft}
\end{minipage} \hfill
\begin{minipage}{0.25\linewidth}
  \begin{flushleft}
    Course: AIMA 104 \\
    Semester: II \\
    F.M. : 20
  \end{flushleft}
\end{minipage}
\vskip 2mm
\rule{\textwidth}{1pt}
\vskip 2mm
\begin{questions}
\question For a matrix $A$ of order $m \times n$. Show that $Null(A)$ is a subspace of $\mathbb{R}^n$. [2]
  \begin{center}
    \bfseries OR
  \end{center}
  For a matrix $A$ of order $m \times n$. Show that the eigenspace $E_{\lambda}$ of its eigenvalue $\lambda$ is a subspace of $\mathbb{R}^n$. [2]

@@

  \question Describe the transformation of the following matrix geometrically:
  $\begin{bmatrix}
    1 & 0\\
    0 & 0
  \end{bmatrix}$. [2]
\end{questions}
\vspace{2cm}
%---------------------------------------------------------------------------------------------------------------------------------
\begin{center}
 {\bfseries  {\large Kathmandu University}} \\
 First In-Semester Exam-2025\\[-1mm]
 {\small \textbf{Department of Artificial Intelligence, Panchkhal}}
\end{center}
\begin{minipage}{0.70\linewidth}
  \begin{flushleft}
    Level: B.Tech Artificial Intelligence \\
    Year: I \\
    Time: 60 minutes
  \end{flushleft}
\end{minipage} \hfill
\begin{minipage}{0.25\linewidth}
  \begin{flushleft}
    Course: AIMA 104 \\
    Semester: II \\
    F.M. : 20
  \end{flushleft}
\end{minipage}
\vskip 2mm
\rule{\textwidth}{1pt}
\vskip 2mm

\begin{questions}
\question For a matrix $A$ of order $m \times n$. Show that $Null(A)$ is a subspace of $\mathbb{R}^n$. [2]
  \begin{center}
    \bfseries OR
  \end{center}
  For a matrix $A$ of order $m \times n$. Show that the eigenspace $E_{\lambda}$ of its eigenvalue $\lambda$ is a subspace of $\mathbb{R}^n$. [2]

  \question Describe the transformation of the following matrix geometrically:
  $\begin{bmatrix}
    1 & 0\\
    0 & 0
  \end{bmatrix}$. [2]
\end{questions}
\newpage

\begin{questions}
  \setcounter{question}{3}
\question Prove: The transformation $T: V \to W$ is linear, then $T(0)=0$. [2]

@@

\question Solve: \hspace{2mm} $x_2+4x_3 = -5, \hspace{5mm} x_1+3x_2+5x_3 = -2, \hspace{5mm} 3x_1 + 7x_2 + 7x_3 = 6$. [4]
\end{questions}
\vspace{9cm}

\begin{questions}
  \setcounter{question}{3}
\question Prove: The transformation $T: V \to W$ is linear, then $T(0)=0$. [2]

\question Solve: \hspace{2mm} $x_2+4x_3 = -5, \hspace{5mm} x_1+3x_2+5x_3 = -2, \hspace{5mm} 3x_1 + 7x_2 + 7x_3 = 6$. [4]
\end{questions}
\end{document}

### 2025-06-16 question_papers/aima104_mcq_first_in_sem.tex
question_aima104

\begin{minipage}{0.70\linewidth}
  \begin{flushleft}
    Level: B.Tech Artificial Intelligence \\
    Year: I \\
    Time: 15 minutes
  \end{flushleft}
\end{minipage} \hfill
\begin{minipage}{0.25\linewidth}
  \begin{flushleft}
    Course: AIMA 203 \\
    Semester: II \\
    F.M. : 10
  \end{flushleft}
\end{minipage}
\vspace{-8mm}
\begin{center}
  \rule{\textwidth}{1pt}
  Roll No: \hspace{5.5cm} Marks Scored:
  \vskip -3mm
\rule{\textwidth}{1pt}
\end{center}

\begin{center}
  SECTION''A'' \hspace{5mm} [10 Q \(\times\) 1 = 10 marks] (\textit{Do any ten}).
\end{center}
Fill in the blanks by writing the most appropriate word(s) or symbol(s).
\begin{questions}
\question Give an example of a vector and its scalar. \rule{7cm}{0.15mm}.
\question Give an example of a subspace of $\mathbb{R}^2$ : \rule{8cm}{0.15mm}.

@@

\question Write the basis of the vector space ${0}$. \rule{7cm}{0.15mm}.

 \question Suppose a $4 \times 7$ matrix $A$ has four pivot columns. Is $Col(A) = \mathbb{R}^4$? Is $Nul(A) = \mathbb{R}^3$ ?
\end{questions}

>>>>

\begin{minipage}{0.70\linewidth}
  \begin{flushleft}
    Level: B.Tech Artificial Intelligence \\
    Year: I \\
    Time: 15 minutes
  \end{flushleft}
\end{minipage} \hfill
\begin{minipage}{0.25\linewidth}
  \begin{flushleft}
    Course: AIMA 203 \\
    Semester: II \\
    F.M. : 10
  \end{flushleft}
\end{minipage}
\vspace{-8mm}
\begin{center}
  \rule{\textwidth}{1pt}
  Name: \hspace{5cm}  Roll No: \hspace{3cm} Marks-Scored:
  \vskip -3mm
\rule{\textwidth}{1pt}
\end{center}

\begin{center}
  SECTION''A'' \hspace{5mm} [10 Q \(\times\) 1 = 10 marks] (\textbf{\textit{Do any ten}}).
\end{center}
Fill in the blanks by writing the most appropriate word(s) or symbol(s).
\begin{questions}
\question Give an example of a vector and its scalar. \rule{7cm}{0.15mm}.
\question Give an example of a subspace of $\mathbb{R}^2$ : \rule{8cm}{0.15mm}.

@@

\question Write a basis of the vector space $\{0\}$. \rule{7cm}{0.15mm}.

\question Suppose a $4 \times 7$ matrix $A$ has four pivot columns. Is $Col(A) = \mathbb{R}^4$? Is $Nul(A) = \mathbb{R}^3$ ? \rule{12cm}{0.15mm}.

\question Is the set of vectors linearly dependent?$\{(1,2, 4) \;\; (2,4,8)\}$ \rule{4cm}{0.15mm}.

\question What are the eigenvalues of a triangular matrix? \rule{7cm}{0.15mm}.

\question Explain why there are infinitely many eigenvalues associated with an eigenvalue.\\[1mm]
  \rule{12cm}{0.15mm}.

\question If $Ax=2x$ then, $AAx=?$ \rule{7cm}{0.15mm}.

\question Can you explain the case where zero is an eigenvalue of a matrix? \\[1mm] \rule{12cm}{0.15mm}.
\end{questions}
